Sampling requirements to detect ecosystem change

### 2020-06-18 R/manuscript_draft.Rmd
edit to the manuscript post review. Starting a paragraph on what has already been done, and what is our specific contribution.

>>>>

Two dimensions are to be considered when sampling: spatial and temporal dimension. To estimate a same parameter, population abundance, optimal spatial sampling strategies are based on spatially balanced sampling [@kermorvant_optimizing_2019], while optimal temporal sampling strategies are more cost efficient with a targeted sampling, e.g., around the period of reproduction [@jackson_sampling_2008]. _Add at least another sentence here to make the transition to our work, but right now I can't think of a good formulation_
